\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
\usepackage{fontawesome}

% personal data
\name{Alexey}{Romanov}
\address{Zelenograd}{Moscow}{Russia}               % optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
%\phone[mobile]{+7~(234)~567~890}
\email{alexey.v.romanov@gmail.com}
\social[linkedin]{alexeyromanov}                        % optional, remove / comment the line if not wanted
\social[twitter]{alexey_r}
\social[github]{alexeyr}
\extrainfo{%
\faStackOverflow~\httplink[Alexey Romanov]{stackoverflow.com/users/9204/alexey-romanov}%
}
\begin{document}
\makecvtitle

\section{Education}
\cventry{1998--2003}{Specialist in Applied Mathematics}{Moscow State University}{Moscow}{Diploma with honours (Red diploma)}{Specialization: Mathematics, Mathematical Logic}

\section{Objective and Summary}
I am interested in working as a Senior Software Engineer on challenging projects. I am an experienced JVM developer (primarily using Scala and Kotlin) with excellent knowledge of algorithms and data structures. I also have some experience in native languages (C++, Rust, C) and web programming.

\section{Professional Skills}
\subsection{Primary}
\cvlistitem{Languages: C++, Scala, Kotlin, Java, Erlang, Python}
\cvlistitem{Algorithms and data structures}
\cvlistitem{Concurrent and parallel programming}
\cvlistitem{Teaching, mentoring}
\subsection{Intermediate}
\cvlistitem{Languages: Rust, SQL, C\#, Haskell, JavaScript, Prolog, Ruby}
\cvlistitem{Databases (particularly SQLite)}
\cvlistitem{Compilers, optimizations, code transformation}
\cvlistitem{Machine Learning}
\cvlistitem{OSGi, Eclipse RCP}
\cvlistitem{IDEA/Android Studio plugin development}
\subsection{Basic}
\cvlistitem{Languages: C, OCaml, Lua, Scheme/Racket, TypeScript}
\cvlistitem{Android development}

\section{Employment History}
\cventry{2003--present}{Assistant Professor}{Moscow Institute of Electronic Technology}{Zelenograd}{}{}
\cvlistitem{Developed and taught new courses: 
	\begin{itemize}
		\item Mathematical Logic and Algorithm Theory
		\item Functional Programming (using Haskell)
		\item Functional and Logical Programming (using Erlang and Prolog)
	\end{itemize}}
\cvlistitem{Supervised master students}
\cvlistitem{Coauthor of 2 textbooks}

\cventry{2010--2012}{Developer, Lead Developer}{Focus-Media}{Zelenograd}{}{Software development and integration}

\cventry{2013}{Software Architect}{Likemelody LLC}{Zelenograd}{}{Natural language processing software}

\cventry{2013--present}{Key Project Engineer}{Huawei Research}{Moscow}{}{}

\section{Main Projects}

\subsection{At Huawei Russian Research Institute}
\cventry{2013--2016}{Scalan}{}{}{}{A domain-specific optimization and specialization framework}
	\cvlistitem{One of main developers of Scalan framework and a Scala compiler plugin for this framework.}
	\cvlistitem{Coauthor of a WGP2014 paper, patent filed.}
	\cvlistitem{Skills: Scala, Compilers, Optimization, Code transformation}

\cventry{2016}{SQLite Kernel Engine}{}{}{}{An approach to SQLite query optimization}
	\cvlistitem{Lua and C++ code generation from SQL queries, SQLite calls generated code instead of its own bytecode interpreter when detecting a repeated query.}
	\cvlistitem{1.5 to 10x speedup on some queries, patent filed.}
	\cvlistitem{Skills: Scala, C++, Lua, Compilers, Optimization, Code transformation}
	
\cventry{2016}{SQLite Kernel Engine IDEA Plugin}{}{}{}{IDE plugin for integration with SQLite Kernel Engine}
	\cvlistitem{One of two developers of IDEA plugin integrating with SQLite Kernel Engine to provide queries to generate native code for and generate Java API to call these queries.}
	\cvlistitem{Skills: Java, IDEA plugins, Android, Code generation}
	
\cventry{2017--2021}{Open-Source Team}{}{}{}{Contributions to open-source projects}
	\cvlistitem{C++ API for Rust-based Tokenizers library, a new check in clang-tidy, bug fixes contributed to PyTorch, TensorFlow, seqeval, TVM, DMLC.}
	\cvlistitem{Skills: C++, Python, Rust, Compilers, Optimization, Machine Learning}

\cventry{2019--2020}{Fused Transformer}{}{}{}{Native C++ Transformer implementation}
	\cvlistitem{Main developer of a full native C++ Transformer implementation for Android and desktop.}
	\cvlistitem{Slight speedup compared with CPU Tensorflow/PyTorch on desktop, performance on par with ONNX Runtime on device. Project ended before GPU support could be implemented.}
    \cvlistitem{Skills: C++, Python, Machine Learning, SIMD}
	
\cventry{2021--2022}{Panda VM Verifier}{}{}{}{}
	\cvlistitem{Panda VM is Huawei's alternative to Android ART for use in Harmony OS and on server/desktop.}
	\cvlistitem{Bytecode verifier verifies bytecode validity before running it: type correctness, lack of illegal jumps, etc.}
	\cvlistitem{~40\% speedup overall, significant bug fixes and code clean-ups}
    \cvlistitem{Skills: C++, Compilers}

\subsection{Outside Huawei}
\cventry{2010--2014}{erlang-sqlite3}{Focus-Media, then side-project}{}{}{An Erlang library for work with SQLite3 databases}
	\cvlistitem{Took over maintenance and development of an abandoned Erlang library for working with SQLite3 databases. Attracted users and contributors.}
	\cvlistitem{used in projects inside Focus-Media and by external developers}
	\cvlistitem{Skills: Erlang, C, SQLite, Optimization}
	
\cventry{2010--2012}{FocusPlay}{Focus-Media}{}{}{A system for automatically downloading and playing video on remote devices}
	\cvlistitem{Responsible for developing the client side scheduling and processing, assisted with server side.}
	\cvlistitem{Stable processing, successful deployment to multiple satisfied customers.}
    \cvlistitem{Skills: Erlang, C, Java, Network programming, Concurrent programming, Optimization}
	
\cventry{2011--2012}{Several Eclipse RCP projects}{Focus-Media}{}{}{}
	\cvlistitem{Developer on a SCADA system, responsible for aggregating sensor data timeseries, allowing and processing user queries on the data. Developer on automated workplace in a security system.}
	\cvlistitem{Skills: Scala, Java, OSGi, Eclipse RCP, Network programming, UI design}
	
\cventry{2013}{A phone customer service system}{LikeMelody LLC}{}{}{}
	\cvlistitem{Architect and developer on a system automating first-line phone call center for small business.}
	\cvlistitem{Unreleased when I left the company.}
	\cvlistitem{Skills: Natural Language Processing, Machine Learning, Artificial Intelligence}
	
\section{Languages}
\cvitemwithcomment{Russian}{Native}{}
\cvitemwithcomment{English}{Fluent (written), Advanced (spoken)}{}


\section{Patents}
	\cvlistitem{Hongbo Zhang, Alexander Slesarenko, Alexey Romanov. \textit{A system and method for constructing rewrite rules in DSL compilers}. 2014.}
	\cvlistitem{Alexander Slesarenko, Alexey Romanov, Dmitry Vyal. \textit{A system and a method for application-specific query execution in DBMS}. 2016.}

\section{Publications}
	\cvlistitem{Alexey Romanov. \textit{De Jongh and Glivenko theorems for equality theories}. Journal of Applied Non-Classical Logics, 2007}
	\cvlistitem{Alexander Slesarenko, Alexander Filippov, Alexey Romanov. \textit{First-class Isomorphic Specialization by Staged Evaluation}. WGP2014}
	\cvlistitem{Alexander Slesarenko, Alexey Romanov. \textit{Scalan: a Framework for Domain-Specific Hotspot Optimization (Invited Tutorial)}. FHPC2015}

\end{document}
